\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-01-26 papers/jss/article.Rnw
sentence style in captions
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@852 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

% MS: I think this looks better at the bottom of the page.
% so it appears after the new section starts where it is referenced.
\begin{table}[bp]
\centering
\begin{tabular}{lccl}
\toprule
\textbf{Class}      & 
     \textbf{Slots} & 
     \textbf{Methods} & 
     \textbf{Dynamic Dispatch}\\
\cmidrule{1-4}
Message             & 2 & 20 & yes (field names)\\
Descriptor          & 2 & 16 & yes (field names, enum types, nested types)\\
FieldDescriptor     & 4 & 18 & no\\
EnumDescriptor      & 4 & 11 & yes (enum constant names)\\
FileDescriptor      & 3 & \phantom{1}6 & yes (message/field definitions)\\
EnumValueDescriptor & 3 & \phantom{1}6 & no\\
\bottomrule
\end{tabular}
\caption{\label{class-summary-table}Overview of Class, Slot, Method and
  Dispatch Relationships}
\end{table}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\textwidth]{figures/histogram-mapreduce-diag1.pdf}
\end{center}
\caption{Diagram of MapReduce Histogram Generation Pattern}
\label{fig:mr-histogram-pattern1}
\end{figure}

>>>>

% MS: I think this looks better at the bottom of the page.
% so it appears after the new section starts where it is referenced.
\begin{table}[bp]
\centering
\begin{tabular}{lccl}
\toprule
\textbf{Class}      & 
     \textbf{Slots} & 
     \textbf{Methods} & 
     \textbf{Dynamic Dispatch}\\
\cmidrule{1-4}
Message             & 2 & 20 & yes (field names)\\
Descriptor          & 2 & 16 & yes (field names, enum types, nested types)\\
FieldDescriptor     & 4 & 18 & no\\
EnumDescriptor      & 4 & 11 & yes (enum constant names)\\
FileDescriptor      & 3 & \phantom{1}6 & yes (message/field definitions)\\
EnumValueDescriptor & 3 & \phantom{1}6 & no\\
\bottomrule
\end{tabular}
\caption{\label{class-summary-table}Overview of class, slot, method and
  dispatch relationships}
\end{table}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\textwidth]{figures/histogram-mapreduce-diag1.pdf}
\end{center}
\caption{Diagram of MapReduce histogram generation pattern}
\label{fig:mr-histogram-pattern1}
\end{figure}
